---
title: "Assingment-1"
author: "KAMESHWARAN R"
date: "2023-07-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1.This exercise involves the Auto data set studied in the lab. Make sure that the missing values have been removed from the data.


 (a) Which of the predictors are quantitative, and which are qualitative?

```{r}
library(ISLR)
```

```{r}
Auto= na.omit(Auto)
?Auto

```
(b) What is the range of each quantitative predictor? You can answer this using the range() function.

```{r}
range(Auto[,1])
for (i in c(1,3,4,5,7)){
  print(range(Auto[,i]))
}

```

(c) What is the mean and standard deviation of each quantitative predictor? 

```{r}
range(Auto[,1])
for (i in c(1,3,4,5,7)){
  print(mean(Auto[,i]))
}
```
```{r}
range(Auto[,1])
for (i in c(1,3,4,5,7)){
  print(sd(Auto[,i]))
}
```


(d)	 Now remove the 10th through 85th observations. What is the range, mean, and standard deviation of each predictor in the subset of the data that remains? 

```{r}
data = Auto[-(10:85),]
View(data)

names(Auto)

```

(e)	Using the full data set, investigate the predictors graphically, using scatterplots or other tools of your choice. Create some plots highlighting the relationships among the predictors. Comment on your findings.

```{r}
 pairs(Auto[,1:7],col="blue")

```

(f) Suppose that we wish to predict gas mileage (mpg) on the basis of the other variables. Do your plots suggest that any of the other variables might be useful in predicting mpg? Justify your answer

Ans:Yes The factors are more likely to be helpful in forecasting the target variable (such as miles per gallon, or mpg), if they exhibit a distinct pattern or trend in the data. Conversely, the factors are less likely to be useful for prediction if there is no obvious relationship between them.

Relationship type also matters. In comparison to a nonlinear relationship, a linear relationship is simpler to model and forecast.

A strong inverse relationship exists between placement, horsepower, and weight and mpg.

